### 2023-10-06 3.Design/dataset.tex
Adding stuff to celegans model/problem
Changed one detail

>>>>

\begin{itemize}
  \item An \ac{LSTM} with eight hidden states ($n_h=8$) and an input with feature size of four (because of the four input neurons that are considered), one thousand time steps and every time steps outputs a value for the next layer.
  \item A time distributed dense layer with an output size of four. It is time distributed because it needs to compute every time steps and not only the last.
\end{itemize}

\Cref{fig:celegansModel} is a graphical representation of the model just described.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{datasets/celegansModel}
  \caption{Model used to solve the \ac{C. elegans} problem}
  \label{fig:celegansModel}
\end{figure}
